\textbf{ANALYSIS OF \\ NEURAL NETWORKS \\ APPLIED TO CONNECT FOUR} \\[0.5cm] \rule{10cm}{0.3mm} \\[0.5cm] \small \scshape{A closer look into the intricacies of artificial neural networks} \\[0.4cm] \rule{10cm}{0.3mm} \vskip -0.3cm

### 2023-03-19 doc/paper.tex
add tex files for paper.pdf

\vskip 5cm

@@

\begin{figure}[h]
    \center
    \includegraphics[scale=0.52]{Q-K4-L10-R5_vs_mcts2000}
    \caption{Convolutional neural network with kernel size 4 against MCTS-2000}
\end{figure}

@@

\noindent
The first phenomenon noticeable in the data presented by the diagrams in Figures 27, 28 and 29, is \emph{catastrophic inference}, also referred to as \emph{catastrophic forgetting} \cite{catastrophic}. Notice the very sudden spikes in win rate for each of the neural networks followed by sudden drops in win rate. This pattern seems to repeat itself through the generations and it almost seems like the neural networks at some points learn how to win games but then suddenly forget what they have learnt. This is what we call catastrophic forgetting, which is defined as a tendency of a neural network to abruptly and drastically forget previously learnt information up learning new information \cite{catastrophic}. It is generally a challenge to create a neural network that is sensitive enough to detect small details, such as patterns in the Connect Four board, without being disrupted by new information \cite{catastrophic}. Catastrophic forgetting occurs when many of the weights that have been adjusted and learnt something, for example, the pattern of 3 tokens of the same color in a line, are changed by new data instances. It then becomes unlikely that the weights still "remember" what they had learnt previously since the latest information is being superimposed on top of the old information.

@@

This paper studies the impact different parameters have on the learning of simple neural networks. In practice, most neural networks are significantly more complex and take a lot more time and better data to be trained well. It is then even more important to choose the parameters we present in this paper with care in order to improve the accuracy of the neural networks as well as minimise the amount of time spent training them. The results of this paper could therefore be used to train more sophisticated neural networks with more certainty and less time, which naturally aids the development and research of neural networks. A way to further develop this project, one could analyze how the parameters impact the performance of the neural networks when varied in combination with each other. A larger local receptive field of a convolutional neural network could for example benefit from a smaller learning rate in comparison to a smaller receptive field. Another way to continue this project would be by studying ways to prevent catastrophic inference, which our neural networks were subjected to quite often.

>>>>

@@

\begin{figure}[h]
    \center
    \includegraphics[scale=0.52]{DQ-K4-L10-R5_vs_mcts2000}
    \caption{Convolutional neural network with kernel size 4 against MCTS-2000}
\end{figure}

@@

\noindent
The first phenomenon noticeable in the data presented by the diagrams in Figures 27, 28 and 29, is \emph{catastrophic interference}, also referred to as \emph{catastrophic forgetting} \cite{catastrophic}. Notice the very sudden spikes in win rate for each of the neural networks followed by sudden drops in win rate. This pattern seems to repeat itself through the generations and it almost seems like the neural networks at some points learn how to win games but then suddenly forget what they have learnt. This is what we call catastrophic forgetting, which is defined as a tendency of a neural network to abruptly and drastically forget previously learnt information up learning new information \cite{catastrophic}. It is generally a challenge to create a neural network that is sensitive enough to detect small details, such as patterns in the Connect Four board, without being disrupted by new information \cite{catastrophic}. Catastrophic forgetting occurs when many of the weights that have been adjusted and learnt something, for example, the pattern of 3 tokens of the same color in a line, are changed by new data instances. It then becomes unlikely that the weights still "remember" what they had learnt previously since the latest information is being superimposed on top of the old information.

@@

This paper studies the impact different parameters have on the learning of simple neural networks. In practice, most neural networks are significantly more complex and take a lot more time and better data to be trained well. It is then even more important to choose the parameters we present in this paper with care in order to improve the accuracy of the neural networks as well as minimise the amount of time spent training them. The results of this paper could therefore be used to train more sophisticated neural networks with more certainty and less time, which naturally aids the development and research of neural networks. A way to further develop this project, one could analyze how the parameters impact the performance of the neural networks when varied in combination with each other. A larger local receptive field of a convolutional neural network could for example benefit from a smaller learning rate in comparison to a smaller receptive field. Another way to continue this project would be by studying ways to prevent catastrophic interference, which our neural networks were subjected to quite often.
